A Triangle Mesh Approach to Painting

### 2014-04-21 template.tex
Added the zoom level
Added teaser with rainbow image.

%% \teaser{
%%   \includegraphics[height=1.5in]{images/sampleteaser}
%%   \caption{Spring Training 2009, Peoria, AZ.}
%% }

@@

\begin{figure*}
    \centering
        \includegraphics[width=0.195\textwidth]{images/zoom61}
        \includegraphics[width=0.195\textwidth]{images/zoom62}
        \includegraphics[width=0.195\textwidth]{images/zoom63}
        \includegraphics[width=0.195\textwidth]{images/zoom64}
        \includegraphics[width=0.195\textwidth]{images/zoom65}
        \includegraphics[width=0.195\textwidth]{images/zoom66}
        \includegraphics[width=0.195\textwidth]{images/zoom67}
        \includegraphics[width=0.195\textwidth]{images/zoom68}
        \includegraphics[width=0.195\textwidth]{images/zoom69}
        \includegraphics[width=0.195\textwidth]{images/zoom71}
    \caption{A painting that shows extreme zoom levels.  The final image is at \Steve{zoom level XXX}.}
    \label{fig:boxes}
\end{figure*}

>>>>

\teaser{
  \setlength{\w}{0.33\textwidth}
  \centering
  \includegraphics[width=\w]{images/rainbow3}
  \includegraphics[width=\w]{images/rainbow3_tri}
  \includegraphics[width=\w]{images/rainbow3_zoom3}
  \caption{A vector painting made in TrianglePaint that exhibits smooth gradients painted by soft brushes, as well as infinitely sharp boundaries painted by hard brushes, together in a single flat representation.  The triangle mesh is shown in the middle, and the right image is zoomed in on the bottom of the letter B, to show the sharp boundaries and smooth gradients in detail.}
  \label{fig:teaser}
}

@@

\begin{figure*}
    \centering
        \includegraphics[width=0.195\textwidth]{images/zoom61}
        \includegraphics[width=0.195\textwidth]{images/zoom62}
        \includegraphics[width=0.195\textwidth]{images/zoom63}
        \includegraphics[width=0.195\textwidth]{images/zoom64}
        \includegraphics[width=0.195\textwidth]{images/zoom65}
        \includegraphics[width=0.195\textwidth]{images/zoom66}
        \includegraphics[width=0.195\textwidth]{images/zoom67}
        \includegraphics[width=0.195\textwidth]{images/zoom68}
        \includegraphics[width=0.195\textwidth]{images/zoom69}
        \includegraphics[width=0.195\textwidth]{images/zoom71}
    \caption{A painting that shows extreme zoom levels.  The final image is at zoom level 93,000.}
    \label{fig:boxes}
\end{figure*}
